\documentclass[12pt]{article}

\usepackage[letterpaper]{geometry}

\newcommand{\sj}{}

\title{Cleary, Holt, Cox revisions}
\author{Michelle Jones, Samuel Johnson}

\begin{document}
\section*{Paper 1}

\subsection*{Plan}

\begin{itemize}
  \item Finish reading (Sam)
  \item Rewrite Introduction - define clear question and hypothesis
  \item Lit review - Start with Feenstra and McGarvey
  \item Strip aquaculture
  \item strip CPUE??
  \item Merge data sets (Michelle)
  \item Run and understand code/model
    \begin{itemize}
      \item For their data
      \item for our data
      \item for combined data
    \end{itemize}
  \item Start with aggregated data (ignore age/size structure)
  \item Analyse and then decide

\end{itemize}

\subsection*{Methods}
\begin{itemize}
  \item What is the data we need?
    \begin{itemize}
      \item Individual recovery lat and long
      \item If not possible, recovery by STRS area across all survey designs
    \end{itemize}
  \item What is the data we have?
  \item What can it tell us?
  \item How can we get it to tell us this?
\end{itemize}


\section*{Paper 2}

\subsection*{Question: What is the inlet stock size?}
\subsubsection*{Sub-qestion: What is the contribution to offshore fisheries?}

\subsection*{Methods}
\begin{itemize}
  \item What is the data we need?
    \begin{itemize}
      \item Individual recovery lat and long
      \item If not possible, recovery by STRS area across all survey designs
      \item CPUE spatially explicit in 3d (lat, long, depth)
    \end{itemize}
  \item What is the data we have?
  \item What can it tell us?
    \item What is the (relative) abundance of sablefish in nearshore inlets
  \item How can we get it to tell us this?
    \begin{itemize}
      \item Jolly Seber (or some variant)
    \end{itemize}
\end{itemize}


\end{document}